An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2013-02-06 Paper.tex
Tweak wording in reference to McCracken (2000)
One of the results for the supplemental appendix claims that the proof procedes
pretty much exactly as in McCracken.  I tweaked the wording.

\begin{lema}\label{res:a5}
  If the conditions of Theorem~\ref{res:3} hold\footnote{The
    assumptions governing $\hat{\beta}_t^{*}$ are unnecessary.} then
  \begin{equation}
    \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
    (f_{t}(\hat{\beta}_{t}) - \E f_{t}(\beta_{0})) \to^d N(0, \Omega),
  \end{equation}
  with $\Omega$ given in \citet[Theorem 2.3.1]{Mcc:00}.
\end{lema}
\begin{proof}[Proof of Lemma~\ref{res:a5}]
  The proof follows exactly as in \citet[Theorem 2.3.1]{Mcc:00}.
\end{proof}

>>>>

\begin{lema}\label{res:a5}
  If the conditions of Theorem~\ref{res:3} hold\footnote{The
    assumptions governing $\hat{\beta}_t^{*}$ are unnecessary.} then
  \begin{equation}
    \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
    (f_{t}(\hat{\beta}_{t}) - \E f_{t}(\beta_{0})) \to^d N(0, \Omega),
  \end{equation}
  with $\Omega$ given in \citet[Theorem 2.3.1]{Mcc:00}.
\end{lema}
\begin{proof}[Proof of Lemma~\ref{res:a5}]
  The proof follows exactly as in \citet[Theorem 2.3.1]{Mcc:00}, using
  the previous results in this appendix as substitutes where the
  original proof requires stronger moment or weak dependence
  conditions.
\end{proof}
